% Thank you Sourabh Bajaj for this template.
%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
  \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
    \textbf{#1} & #2 \\
    \textit{\small#3} & \textit{\small #4} \\
  \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}
\renewcommand{\labelitemiii}{--}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\newcommand{\resumeItemDescpritionStart}{\begin{itemize}}
\newcommand{\resumeItemDescpritionEnd}{\end{itemize}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{\href{http://onkars.me/}{\Large Onkar Shedge}} & Email : \href{mailto:oshedge@outlook.com}{oshedge@outlook.com}\\
\href{https://iamonkar.dev/}{https://iamonkar.dev/} & Mobile : +91 7276867872 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{Pune Institute of Computer Technology}{Pune, India}
{Bachelor of Computer Engineering;  GPA: 3.66 (9.15/10.0)}{Aug. 2012 -- July. 2016}
\resumeSubHeadingListEnd

%-----------Objective-----------------
\section{Objective}
In my professional experience, I have worked in an environment which follows Agile, Extreme Programming practices. I have learnt to write clean code, TDD; worked on backend, DevOps.
I am interested in Distributed systems, DDD. In an effort to enhance my knowledge and contribute to organization's growth, I'd like to bring these skills to the mentioned position.

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{ThoughtWorks}{Pune, India}
{Application Developer}{August 2016 - November 2020}
\resumeItemListStart

\resumeItem{Capital Management Finance Application}
{Tool to capture and maintain holdings for multiple capital assets for partners.
Provide an updated view to the user along with picture perfect reports and even ad-hoc analysis.
Very critical application since this is the only source of truth for a partner's holding.}
\break
I worked on the following technologies in the project :
\resumeItemDescpritionStart
\item Backend: MiroServices, Spring Boot 2.1, Java 11, Mysql 8, helm, k8s, GoCD pipelines
\item Monitoring \& Logging:  Build dashboards, alerts in Splunk. Metric collection using Prometheus and visualization in Grafana.
\item Data Migration: Migrated data from legacy application's Oracle DB to Mysql 8 using Sqlines, Pentaho and tested using Querysurge.
\item ETL: ETL of data from application to reporting using Pentaho, run using Kubertenes Jobs
\item Spring-Batch for batch transactions.
\item Frontend: Worked to some extent: React 16(React hooks), Redux, Ag-grid.
\resumeItemDescpritionEnd

\resumeItem{Retail pricing solution}
{Price recommendation system for products placed on the shelf. The application comprised of human intelligence and Data Science. Apart from writing Scala API's, I also worked on Data Engineering to some extent.}
\resumeItemDescpritionStart
\item Aiflow as workflow-manager/orchestrator.
\item Spark Jobs deployed on GCP DataProc cluster.
\item Scala 2.12, Play Framework, Postgres, Kubernetes.
\resumeItemDescpritionEnd

\resumeItem{ETL Application}
{The goal of the application was to get data(around 250Gb) from Salesforce and dump it into AWS Redshift via S3 using \textit{COPY} command. Analysts used this data for visualizations in Tableau. }
\resumeItemDescpritionStart
\item Created a Kubernetes job from within the cluster, using RBAC.
\item Used Celery to speed up the downloading data from Salesforce.
\item Refactored synchronous API requests to asynchronous using asyncio.
% \item Gave a office wide lunch and learn on Authentication and authorization in k8s, to share and extend my knowledge on k8s, demoed on AWS using kops to deploy.
\item Python3, Flask, React, Redux, K8s, helm, circleCI.
\resumeItemDescpritionEnd

\resumeItem{Bumblebee Chatbot (Internal Application)}
{Created a chatbot as a platform so that other teams can develop their features into the bot. Integrated with \href{https://chat.google.com}{chat.google}
}
\resumeItemDescpritionStart
\item Tool used: API.ai now known as Dialogflow.
\item Got familiar with AWS services like AWS lambda, DynamoDB, IAM roles and JWT tokens, Oauth2.
% \item Also created a personal chatbot integrated with google's personal assistant to book meeting rooms and find when a person is free/busy. Was closely monitoring events in Google I/O 2017 for updates.
\item Golang 1.8, CircleCI
\resumeItemDescpritionEnd

\resumeItemListEnd




\resumeSubheading
{Pune Institute of Computer Technology}{Pune, India}
{Student}{Aug 2012 - May 2016}
\resumeItemListStart
\resumeItem{Distributed Off-heap JVM Cache}
{Interned at eQ Technologic. Stored large data, replicated across cluster, in JVM off-heap inspired by HDFS architecture. }
\resumeItem{Pradnya Competition}
{A Django web application, so participants can solve problems by submitting code.}
\resumeItem{Blog}
{In 2nd year wrote a blog on NASM(x86 assembly language progamming) with my colleague. \href{http://nasmcodeasy.blogspot.in/}{http://nasmcodeasy.blogspot.in}
}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Achievements}
\resumeSubHeadingListStart
\resumeSubItem{Google Summer of Code 2016 - Apache Zeppelin}
{Notebooks are stored in the local file-system or cloud. The goal of the project was to share these notebooks with other users via p2p systems like IPFS, Bittorrent
\href{https://onkarshedge.github.io/gsoc2016/}{https://onkarshedge.github.io/gsoc2016/}}
\resumeSubItem{ACM ICPC}
{Participated in ACM ICPC regionals 2015 IIT Kharagpur, secured 71st rank, only team from PICT at that regionals.}
\resumeSubHeadingListEnd


% --------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\item{
\textbf{Languages}{: Java, Python, Scala, JavaScript}
}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
